Verifying Demonstrations

### 2018-05-24 paper/analysis-security.tex
Adds WIP on privacy analysis

\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
indeed on the location when the proof share was created.
Thus we must ensure that Alice cannot forge undeserved witness signatures, which 
is ensured using the same linkability mechanism as above.
To forge a witness signature, Alice must produce a \(\wid'\) such that
\begin{multline*}
  \pi_{\wid', \wsig'}\gets \SPK\left\{ (\sk_W') : \right. \\
    \begin{aligned}
      \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
      \wsig' &= \ACprf[_{\sk_W'}][\wid', t_s, t_s', l] \quad \land \\
      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
    \end{aligned} \\
      (\pid, \wid', t_s, t_s', l, \wsig'),
\end{multline*}
while not knowing a signature on the secret key \(\sk_W'\).
Thus she must get break the \(\AC\) scheme to succeed or get a valid signature 
on \(\sk_W'\) from the \ac{CA}.
(Note that Alice can produce one witness signature for herself, since she has 
access to her own \(\sk_P\), but no more.)

@@

\daniel{Must write up privacy analysis.
  However, must complement the privacy definition for this.}

>>>>

\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
indeed on the location when the proof share was created.
Thus we must ensure that Alice cannot forge undeserved witness signatures, which 
is ensured using the same linkability mechanism as above.
To forge a witness signature, Alice must produce a \(\wid'\) such that
\begin{multline*}
  \pi_{\wid', \wsig'}\gets \SPK\left\{ (\sk_W') : \right. \\
    \begin{aligned}
      \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
      \wsig' &= \ACprf[_{\sk_W'}][\wid', t_s, t_s', l] \quad \land \\
      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
    \end{aligned} \\
      (\pid, \wid', t_s, t_s', l, \wsig'),
\end{multline*}
while not knowing a signature on the secret key \(\sk_W'\).
Thus she must break the \(\AC\) scheme to succeed or get a valid signature on 
\(\sk_W'\) from the \ac{CA}.
(Note that Alice can produce one witness signature for herself, since she has 
access to her own \(\sk_P\), but no more.)

@@

We start with \cref{ProtestUnlink}, that Alice's proofs must be unlinkable 
across protests (but linkable within one protest due to \cref{CountOnce}).
It follows from the properties of \(\ACprf\) that \(\pid = 
  \ACprf[_{\sk_P}][\cid]\) and \(\pid' = \ACprf[_{\sk_P}][\cid']\) are 
unlinkable if \(\cid\neq \cid'\).

Now to \cref{ProofUnlink}.
Say that a witness works for Grace.
This witness interacts with Alice directly, \ie has (physically) identified her.
The witness also learns Alice's \(\pid\), but not \(\cid\), to compute \(\wid\) 
and to verify the \ac{DBPK}.
\daniel{This assumes that I will do the changes to hide \(\cid\) from the 
  witness in the \ac{DBPK}.}
Afterwards, Alice publishes \(\pid\) and \(\cid\) together as part of the proof 
share.
The probability of a colliding \(\pid = \ACprf[_\sk][\cid']\) for some \(\cid' 
  \neq \cid\) and \(\sk \neq \sk_P\) is \enquote{small}.
\daniel{Fix this.}
Now Grace can link \(\cid\) (and thus the opinions in the manifesto) to Alice.
